DisjunctiveProgramming.jl: Generalized Disjunctive Programming Models and Algorithms for JuMP

### 2024-10-04 paper/paper.tex

\subsection{Solution Technique: Reformulation to Mixed-Integer Program}
The simplest example of a linear GDP system is given below, where $Y_i$ is a Boolean indicator variable that enforces the constraints in the disjunct ($Ax \le b$ or $Cx \le d$) when $true$,

@@

Exclusive-OR constraints as the one given in Eq. \eqref{eq:simple_xor} are more generally modeled as $exactly(1,\{Y_1,Y_2\})$.

>>>>

\subsection{Solution Technique: Reformulation to Mixed-Integer Program} \label{reformulation}
The simplest example of a linear GDP system is given below, where $Y_i$ is a Boolean indicator variable that enforces the constraints in the disjunct ($Ax \le b$ or $Cx \le d$) when $true$,

@@

Exclusive-OR constraints as the one used in Section \ref{reformulation} are more generally modeled as $exactly(1,\{Y_1,Y_2\})$.
